Automatic Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-07 paper/paper_new.tex

For the fish \verb|length| property, it is necessary to determine the furthest points from the centroid of the fish in each direction along its major
axis. Since fish are normally measured in a straight line from their snout down the middle of their trunk, every pixel of the fish blob is projected
onto the fish's major axis (as a line through its centroid).
The projection is done by finding the closest point on the
centroid--principal axis line from the pixel's location.
% intersecting the line through the point along the tangent of the principal axis and the aforementioned centroid--principal axis line.
After processing every pixel in the fish blob, computing the distance
between the two furthest projected points gives the length of the fish in pixels. Multiplying this distance by \verb|scale| gives the fish \verb|length| in centimeters.
\begin{comment}
\subsection{Consideration}
Just gonna throw some caveats in here, might be its own section might not
\begin{itemize}
    \item Program falls back to using detectron mask and bbox for metadata generation in the event the mask generation/pixel analysis fails. Failure is defined as never finding a cohesive flood filled mask that covers more than 10\% of the detectron bbox initially. Can provide a statistic on how often this occurs.
\end{itemize}
\end{comment}
\section{Results}
Technicians employed by our team have manually generated the 22 metadata properties deemed crucial to the overall BGNN project~\cite{leipzig2021biodiversity} for a large number of INHS images. \(20,699\) total entries were created by 13 technicians that spanned \(8,398\) unique images. Of these \(8,398\) images, \(7,244\) were both not part of the \verb|detectron| training set and met our current admissibility criteria for \verb|detectron| and pixel processing. We ran the metadata extraction program on these \(7,244\) images.
For the properties of image scale, fish length, and fish bounding boxes
(properties not manually generated),
a random sample of 50 specimens from the set of \(7,244\) were analyzed by
hand for comparison.

>>>>

For the fish \verb|length| property, it is necessary to determine the furthest points from the centroid of the fish in each direction along its major
axis. Since fish are normally measured in a straight line from their snout down the middle of their trunk, every pixel of the fish blob is projected
onto the fish's major axis (as a line through its centroid).
The projection is done by finding the closest point on the
centroid--principal axis line from the pixel's location.
% intersecting the line through the point along the tangent of the principal axis and the aforementioned centroid--principal axis line.
After processing every pixel in the fish blob, computing the distance
between the two furthest projected points gives the length of the fish in pixels. Multiplying this distance by \verb|scale| gives the fish \verb|length| in centimeters.
\begin{comment}
\subsection{Consideration}
Just gonna throw some caveats in here, might be its own section might not
\begin{itemize}
    \item Program falls back to using detectron mask and bbox for metadata generation in the event the mask generation/pixel analysis fails. Failure is defined as never finding a cohesive flood filled mask that covers more than 10\% of the detectron bbox initially. Can provide a statistic on how often this occurs.
\end{itemize}
\end{comment}
\section{Results}
Technicians employed by our team have manually generated the 22 metadata properties deemed crucial to the overall BGNN project~\cite{leipzig2021biodiversity} for a large number of INHS images. \(20,699\) total entries were created by 13 technicians that spanned \(8,398\) unique images. Of these \(8,398\) images, \(7,244\) were both not part of the \verb|detectron| training set and met our current admissibility criteria for \verb|detectron| and pixel processing. We ran the metadata extraction program on these \(7,244\) images.
For the properties of image scale, fish length, and fish bounding boxes
(properties not manually generated),
a random sample of 100 specimens from the set of \(7,244\) were analyzed by
hand for comparison.
